Effects of Unemployment Benefits and Uncertainty in Heterogeneous Models

### 2017-01-22 presentation/presentation.tex
minor changes to presentation.

\documentclass{beamer}
\usepackage{graphicx}
\usepackage{breqn}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{dsfont}
% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

@@

@@

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.5]{log-deviation}}

@@

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.5]{distribution}}

@@

  \centering{\includegraphics[scale=0.5]{meanandmedian}}

@@

  \centering{\includegraphics[scale=0.30]{parameters}}

@@

  \centering{\includegraphics[scale=0.30]{parameters_sigma}}

>>>>

\documentclass{beamer}
\usepackage{graphicx}
\usepackage{breqn}
\graphicspath{ {images/Eric/} }
\usepackage{amsmath}
\usepackage{dsfont}
% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

@@

\begin{frame}{Model overview}
	\begin{itemize}

	\item {
	Ex ante identical individuals are subject to uninsurable idiosyncratic shocks. 
	}
	\item {
Agents can interact on the asset market
	}
	\item {
The model generates an endogenous distribution of wealth across consumers. 
	}	
	\item {
Unlike in the stochastic representative agent model seen in the macro class, individual uncertainty does not coincide with aggregate uncertainty. 
	}
	\item {
Aggregates and prices are jointly determined by the saving behavior of the collection of all hh. 
}

@@

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.45]{log-deviation}}

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.45]{deviations_sigma}}

@@

\begin{frame}{Changes in idiosyncratic risk}
  \centering{\includegraphics[scale=0.45]{distribution}}

@@

  \centering{\includegraphics[scale=0.425]{meanandmedian}}

@@

  \centering{\includegraphics[scale=0.45]{parameters}}

@@

  \centering{\includegraphics[scale=0.45]{parameters_sigma}}
